---
title: "Survival"
author: "Tusar"
date: "2025-02-12"
output: html_document
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(fig.path = 'Figures/', fig.align = 'center',
                      tidy = FALSE)
options(replace.assign = TRUE, width = 75, keep.blank.line = FALSE, digits = 6)

```


We can create a multivariable Cox proportional hazard model with all body composition parameter and select the variable which has strongest impact on overall survival
by using the Akaike Information Criterion (AIC) criteria. 
```{r}

library(survival)
library(MASS)

# Fit the initial model

fit1 <- coxph(Surv(survivalTime, survivalStatus) ~ bone_whole_scan + muscle_whole_scan + toAdiTissue_whole_scan + itmAdiTissue_whole_scan + subAdiTissue_whole_scan + visAdiTissue_whole_scan, data = merged_data)

fit1
```

Performing stepwise selection by the stepAIC function from package MASS.

```{r}
fitAIC <- stepAIC(fit1, trace = FALSE) # direction = "both",
```

Examine the summary to get the variable with the strongest impact.
```{r}
# The summary function provides the result in a comprehensive table.
summary(fitAIC)
```

The bone density volume has the strongest impact on overall survival.

The analysis-of-variance and analysis-of-deviance table summarizes the brief results.

```{r}
anova(fit1)
```


# Software
We used the following software versions to generate this report.
```{r, info, echo=FALSE}
sessionInfo()
```

