---
title: "Missing data"
author: "Tusar"
date: "2025-02-12"
output: html_document
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(fig.path = 'Figures/', fig.align = 'center',
                      tidy = FALSE)
options(replace.assign = TRUE, width = 75, keep.blank.line = FALSE, digits = 6)
```


At first, we load all necessary libraries.
```{r}
library(dplyr)
library(tidyr)
library(kableExtra)

```

Here, we create a function which can calculate the total number and percentage of missing for all variables.


```{r}
missing_func <- function(df) {
  df %>%
    summarise(across(everything(), ~ sum(is.na(.)), .names = "{.col}")) %>%
    pivot_longer(cols = everything(), names_to = "Variable", values_to = "total_Missing") %>%
    mutate(missing_Percentage = (total_Missing / nrow(df)) * 100) %>%
    arrange(desc(total_Missing))
}


```


Run the function in 'merged_data' to get all the necessary aspects of missing values.
```{r}
missing_report <- missing_func(merged_data)
print(missing_report, n = 54)

```

Generating a report in html with all the information of missing data.
```{r}

kable(missing_report, format = "html", caption = "Missing Data Summary") %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

```


# Software
We used the following software versions to generate this report.
```{r, info, echo=FALSE}
sessionInfo()
```


